Growth trajectories: How functional traits influence plant growth

### 2016-08-05 ms/ms-supp.Rnw
Outline of main structure, embed eqn references in table and figure
Allocation model and figures

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-construction cost.}
Data from \citep{Wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to datsa from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/mass_fraction.pdf}
\caption{\textbf{Change in allocation with size.}
\label{f-mass_fraction}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and growth rate changes with plant size.} \label{f-lma_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and relative growth rate changes with plant size.}
\label{f-lma_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and growth rate changes with plant size.} \label{f-rho_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and relative growth rate changes with plant size.}
\label{f-rho_growth_size_relative}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-mass per unit leaf area.}
Data from \citep{Wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to datsa from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/growth_light_dia.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (diameter growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{fig:growth_light_dia}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/growth_light_mass.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (mass growth).} Panels show predicted relationship between
specific trait and mass growth rate, for a plant of specified
mass and under a range of shading environments.
\label{fig:growth_light_mass}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between leaf-mass per unit leaf area
and growth rate changes with plant size.} \label{f-lma_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/lma_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between leaf-mass per unit leaf area
and relative growth rate changes with plant size.}
\label{f-lma_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between wood density
and growth rate changes with plant size.} \label{f-rho_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI/rho_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between wood density
and relative growth rate changes with plant size.}
\label{f-rho_growth_size_relative}}
\end{figure}
